Introducing statistics with `intRo`

### 2016-01-24 jcgs-paper-2016/paper.Rmd
Fix a broken reference

There are seven default modules within \texttt{intRo}, which perform specific data analysis tasks that employ an easy to use point-and-click interface. Each module is placed within a higher level category to further help students navigate the tool. The default modules included in \texttt{intRo} are split into three higher level categories - data, summaries, and statistics - and more modules can easily be added by an instructor, as detailed in section \ref{sec:extensible} and section \ref{sec:modules}. The default modules support uploading and downloading a dataset, transforming variables, graphical and numerical summaries, simple linear regression, contingency tables, and T-tests.

>>>>

There are seven default modules within \texttt{intRo}, which perform specific data analysis tasks that employ an easy to use point-and-click interface. Each module is placed within a higher level category to further help students navigate the tool. The default modules included in \texttt{intRo} are split into three higher level categories - data, summaries, and statistics - and more modules can easily be added by an instructor, as detailed in section \ref{sec:extensible} and section \ref{modules}. The default modules support uploading and downloading a dataset, transforming variables, graphical and numerical summaries, simple linear regression, contingency tables, and T-tests.
